\chapter{Product overview}\label{ch:product-description}

IV-Indicators Nano modules are compact button gauges with an Android-configurable firmware core. Devices are shipped in several variants, each tailored to a specific measurement role:

\begin{itemize}
    \item \textbf{IV-Indicators gauge 3\texttimes{}Pack} --- a bundle containing three indicators that can be programmed individually.
    \item \textbf{IV-Indicators Voltmeter} --- monitors the vehicle charging system and accessory voltage.
    \item \textbf{IV-Indicators Barometer} --- reads oil pressure via a VAG pressure sensor (part number \texttt{03C906051A}).
    \item \textbf{IV-Indicators Thermometer} --- displays coolant or auxiliary temperatures using an NTC thermistor such as Ossca \texttt{01176}.
    \item \textbf{IV-Indicators Lambda} --- interprets narrowband oxygen sensor signals and can be paired with external wideband controllers.
    \item \textbf{IV-Indicators Boost} --- measures boost pressure using a Dacia \texttt{223657266R} (\texttt{161B0004}/\texttt{8200225971}) sensor.
\end{itemize}

Each indicator ships with the following accessories:

\begin{itemize}
    \item Button gauge preloaded with the latest firmware revision.
    \item Socket for harness connection.
    \item External programmer for USB-C/USB-OTG configuration.
\end{itemize}

The programmer connects to an Android phone through a USB-C cable (USB-A adapters and hubs can be used if required). Configuration is also available from a desktop browser using the IV-Conf web pack, described later in this document.
